---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Survtrans

<!-- badges: start -->
[![R-CMD-check](https://github.com/SignorinoY/survtrans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SignorinoY/survtrans/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/SignorinoY/survode/branch/main/graph/badge.svg)](https://app.codecov.io/gh/SignorinoY/survtrans?branch=main)
<!-- badges: end -->

The goal of survtrans is to ...

## Installation

You can install the development version of survtrans from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SignorinoY/survtrans")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(survtrans)
## basic example code
formula <- Surv(time, status) ~ . - group - id
group <- as.factor(sim1$group)
fit <- cv_coxtrans(formula, sim1, group, penalty = "SCAD")
coef(fit)
```

## Code of Conduct
  
Please note that the survtrans project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
