---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Survtrans

<!-- badges: start -->
[![R-CMD-check](https://github.com/SignorinoY/survtrans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SignorinoY/survtrans/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/SignorinoY/survode/branch/main/graph/badge.svg)](https://app.codecov.io/gh/SignorinoY/survtrans?branch=main)
<!-- badges: end -->

The goal of survtrans is to ...

## Installation

You can install the development version of survtrans from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SignorinoY/survtrans")
```

## Example

This is a basic example which shows you how to solve a common problem:

### Multi-Source Survival Analysis

```{r example}
library(survtrans)

formula <- Surv(time, status) ~ . - group - id
group <- as.factor(sim2$group)

# Target learning
fit <- ncvcox(formula, sim2[group == 10, ], lambda = 0.15, penalty = "SCAD")
fit$coefficients

# Group learning
fit <- coxgrp(formula, sim2, group, lambda = 0.02, penalty = "SCAD")
fit$coefficients[, 10]

# Sub-group learning
fit <- coxsg(
  formula, sim2, group,
  lambda1 = 0.07, lambda2 = 0.05, penalty = "SCAD"
)
fit$coefficients[, 10]

# Transfer learning
fit <- coxtl(
  formula, sim2, group, 10,
  lambda1 = 0.04, lambda2 = 0.11, penalty = "SCAD"
)
fit$beta

# Ensemble learning
fit <- coxens(
  formula, sim2, group,
  lambda1 = 0.02, lambda2 = 0.005, penalty = "SCAD"
)
fit$coefficients[, 10]

# Multi-task learning
fit <- coxmtl(
  formula, sim2, group,
  lambda1 = 0.06, lambda2 = 0.06, lambda3 = 0.04, penalty = "SCAD"
)
fit$beta + fit$eta[, 10]
```

## Code of Conduct
  
Please note that the survtrans project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
