---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Survtrans

<!-- badges: start -->
[![R-CMD-check](https://github.com/SignorinoY/survtrans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SignorinoY/survtrans/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/SignorinoY/survtrans/branch/main/graph/badge.svg)](https://app.codecov.io/gh/SignorinoY/survtrans?branch=main)
<!-- badges: end -->

The goal of survtrans is to analyze multi-source survival data with heterogeneous effects. This package provides a set of functions that utilize other data sources to enhance the estimation of the model for the target source.

## Installation

You can install the development version of survtrans from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SignorinoY/survtrans")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(survtrans)
```

### Multi-Sources Survival Analysis
```{r}
formula <- Surv(time, status) ~ . - group - id
```

```{r}
fit <- coxens(
  formula, sim2, sim2$group,
  lambda1 = 0.03, lambda2 = 0.04, lambda3 = 0.01, penalty = "SCAD"
)
summary(fit)
```

## Code of Conduct
  
Please note that the survtrans project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
